Model-based pretreatment for regression with correlated variables.

### 2014-04-16 www/article13.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@541 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

Cross-validation is very time-consuming and thus not friendly with combinatory problematics. Moreover, we need a criterion compatible with structures of different sizes (varying $p_2$) and not related with $Y$ because the structure is inherent to $\boldsymbol{X}$ only. Thus it must be a global criterion.

>>>>

Cross-validation is very time-consuming and thus not friendly with combinatory problematics. Moreover, we need a criterion compatible with structures of different sizes (varying $p_r$) and not related with $\boldsymbol{Y}$ because the structure is inherent to $\boldsymbol{X}$ only. Thus it must be a global criterion.
